Refinements for open pNets

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex
prospectie proprietes?

\subsection{Refinement Relations for automata with the same holes}
\TODO{Hole - = relation pour rabea }

@@

The major challenge in this case is to maintain a form of transitivity while being able to take into account the actions of some of the holes. A naive definition of refinement would ensure that the holes that are identical in the two OAs are taken into account in the simulation. Unfortunately this does not work well with transitivity as if $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no proven property on the way $A_1$ and $A_3$ takes his hole into account, and in general  $A_1$ does not simulate $A_3$. The way we solve this issue is to remember in the simulation relation which holes have been compared. This way the relation is parameterized by the set of holes that belong to the two automata and are taken into account.
In practice, when performing successive refinements, we  keep track of which holes are in common at each step of refinement.
\begin{definition}[Open automata refinement]
For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
\begin{multline*}
	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-10pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}} \\
	\end{array}} \\
	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
\end{multline*}
Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
Hole in \(H\) are called tracked holes.
\end{definition}
It is important to note that every action of the holes outside \(H\) is unconstrained in the related automata.
It is easy to see that the hole-equal simulation is a particular case of openautomata refinement, when  $J_1=J_2=H$.

@@

>>>>

\subsection{Refinement Relations for automata with the same holes}

@@

The major challenge in this case is to maintain a form of transitivity while being able to take into account the actions of some of the holes. A naive definition of refinement would ensure that the holes that are identical in the two OAs are taken into account in the simulation. Unfortunately this does not work well with transitivity as if $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no proven property on the way $A_1$ and $A_3$ takes his hole into account, and in general  $A_1$ does not simulate $A_3$. The way we solve this issue is to remember in the simulation relation which holes have been compared. This way the relation is parameterized by the set of holes that belong to the two automata and are taken into account.
In practice, when performing successive refinements, we  keep track of which holes are in common at each step of refinement.
\begin{definition}[Open automata refinement]
For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
\begin{multline*}
	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-10pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}} \\
	\end{array}} \\
	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
\end{multline*}
Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
Hole in \(H\) are called tracked holes.
\end{definition}
It is important to note that every action of the holes outside \(H\) is unconstrained in the related automata.
It is easy to see that the hole-equal simulation is a particular case of open automata refinement, when  $J_1=J_2=H$.

@@

- reflexivity and transitivity

- composition is a refinement (under which condition?)

- what is the property wrt deadlocks?

- congruence? a[b/j] if $a'$ refines $a$ and if $b'$ refines $b$?

- relation with fh bisimulation
